%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Software Developer} % Job title
    {Nagwa} % Organization
    {Cairo, Egypt} % Location
    {Mar. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of software developers to implement .net core services to automate the process of rendering content files into convenient html format and providing the output to Nagwa web site}
        \item {Enhanced Lua scripts used to render equations in the rendering tool to generate a smaller images on the output html.}
        \item {Oversaw software developers’ progress on applications and applied principles of agile methodologies to keep project on track.}
        % \item {Implemented agile management ideals by facilitating exercises such as sprint planning and team leading standups in order to maintain the delivery process.}
        \item {Implemented several API microservices in .NET Core.}
        \item {Supervising, monitoring, and managing software developers to ensure the quality of the products.}
        % \item {Developing and measuring the individual skills of team members and creating a team structure that allows flexibility.}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
  {Senior Software Developer} % Job title
  {Nagwa} % Organization
  {Cairo, Egypt} % Location
  {June. 2017 - Mar. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Automated the process for localizing educational content to multiple locales in terms of languages, unit systems, currencies, and mathematical notation using C\# tool and LuaLaTeX engine and based on configuration files.}
      \item {Built solution for generating reports about content localization consists of C\# tool and mongo db.}
      \item {Implemented C\# tools for extracting information from data files and generating reports about the educational material.}
      \item {Participated in the development process of HR web application.}
      \item {Collaborated across teams to share information and coordinate on new ideas.}
      \item {Supervised, directed, and supported junior developers in their tasks.}
      \item {Designing and developing large scalable solutions.}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
  {Junior Software Developer} % Job title
  {Nagwa} % Organization
  {Cairo, Egypt} % Location
  {May 2016 - June. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Maintaining and improving existing programs by analyzing and identifying areas for modification.}
      \item {Code debugging and tracing to optimize performance.}
      \item {Writing and maintaining technical documentation to describe program development, logic, coding, testing, changes, and corrections.}
      \item {Constantly staying up-to-date on changing technologies, new tools, computer languages, and new applications to develop internal workflows.}
      \item {Developing software solutions by studying information needs, system flows, data usage, work processes, and investigating problems.}
    \end{cvitems}
  }

%---------------------------------------------------------

\cventry
{Document Engineering Team Leader} % Job title
{Hindawi Publishing Corporation} % Organization
{Cairo, Egypt} % Location
{Dec. 2014 - May 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Liaison between production department and information system department.}
    \item {Assess production department needs for new tools.}
    \item {Work closely with the production teams and information system teams to improve existing tools and maximize opportunities to use information technology to improve the production process/cycle.}
    \item {Analyse production unit processes and trends and advise on best practices and technology tools to enhance the production process.}
    \item {Ensure all aspects of new developed tools meets the needs of the production end users.}
    \item {Monitor software tools after initial release and troubleshoot development problems to figure solutions and resolve them if possible.}  
    \item {Assist in developing new strategic tools to support the production unit to better achieve their targets in terms of quality and quantity}  
    \item {Assess the impact of planned developments on exiting systems, identify risks and roadblocks.}  
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Document Engineering Specialist} % Job title
    {Hindawi Publishing Corporation} % Organization
    {Cairo, Egypt} % Location
    {Sep. 2013 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyze the business for new programs and plugins.}
        \item {Following up the tasks in programs and plugins with programmers.}
        \item {Contacting IT department for handling bugs and new updates.}
        \item {Analyzed operations, business and staff performance, and workflow processes.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Graphics Tester} % Job title
    {Hindawi Publishing Corporation} % Organization
    {Cairo, Egypt} % Location
    {Sep. 2012 - Sep. 2013} % Date(s)
    {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Testing new programs and plugins for debugging.}
      %   \item {Delivering the new programs for Graphics Team and provide support for using the tools.}
      %   \item {Troubleshooting program errors.}
      % \end{cvitems} 
    }
%---------------------------------------------------------
  \cventry
    {Graphic Specialist} % Job title
    {Hindawi Publishing Corporation} % Organization
    {Cairo, Egypt} % Location
    {Dec. 2011 - Sep. 2012} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Operations Coordinator} % Job title
    {New Horizons Computer Learning Centers} % Organization
    {Cairo, Egypt} % Location
    {Dec. 2009 - Dec. 2011} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Front office representative} % Job title
    {New Horizons Computer Learning Centers} % Organization
    {Cairo, Egypt} % Location
    {Dec. 2008 - Mar. 2009} % Date(s)
    {}
%---------------------------------------------------------
  % \cventry
  %   {Internship as a Customer Service Representative} % Job title
  %   {New Horizons Computer Learning Centers} % Organization
  %   {Cairo, Egypt} % Location
  %   {May. 2017 - Mar. 2019} % Date(s)
  %   {}

\end{cventries}
